
```{r}
library(ucimlrepo)
library(corrplot)
```

Load data:
```{r}
MI <- fetch_ucirepo(id = 579)

mi_original = MI$data$original
mi_targets = MI$data$targets

MI$variables$type
```

For complication prediction at the time of admission to hospital, remove the suggested columns:
```{r}
to_remove = c(93, 94, 95, 100, 101, 102, 103, 104, 105)

mi_features = mi_original[ setdiff(2:112, to_remove) ]
```


Building a data frame for making a csv file to share with Alessandro.

```{r}
variable_types = MI$variables$type
mi_df = as.data.frame(mi_original)

mi_df = rbind(variable_types, mi_df)
```


The data contains the following percentages of missing data per column:
```{r, echo = F}
100 * colSums(is.na(mi_features)) / dim(mi_features)[1]
```


Identify continuous variables 
```{r}
var_types = MI$variables$types

mi_features_cont <- mi_features[, (var_types == "Continuous")]

100 * colSums(is.na(mi_features_cont)) / dim(mi_features)[1]
```

Identify numerical columns.(Continuous, Integer, Binary) 
```{r, echo = FALSE, results = 'hide'}
mi_features_num <- mi_features[, sapply(mi_features, is.numeric)]

100 * colSums(is.na(mi_features_num)) / dim(mi_features)[1] 
```

Here we use a simple median imputation to avoid losing too many observations:
```{r}

for(i in 1:ncol(mi_features_num)) {
  mi_features_num[is.na(mi_features_num[,i]), i] <- median(mi_features_num[,i], na.rm = TRUE)
}

tail(mi_features)
```

Scaling was used
```{r, echo = F}
pca <- prcomp(mi_features_num, center = TRUE, scale. = TRUE)

summary(pca)
```

Data seems to be uncorrelated due to low variance in the several principal components, as shown by th corr. plot:

```{r}
R = cor(mi_features_num)
corrplot(R, method = "color", tl.pos = "n")
```

#Questions

What to do with missing values? MICE? missMDA? Some columns have over 90% missing values?
Most of the variables are binary? How to procede? 




```{r}



```



